Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-08 paper/v1.0/abstract.tex
Change abstract paper

Interactions between light and matter have dragged research attention in the fields of optoelectronics, sensing, energy harvesting, quantum computing, bio-information, and in many branches of recent technologies. For many years, the foremost aims for examing the characteristics of dressed fermion systems were focused on the different types of atomic and molecular arrangements. These researches of extreme electron-light engagements introduced an astonishing scope of twentieth-century physics namely quantum optic physics.

>>>>

A generalized mathematiocal model for the transport properties of  systems exposed to a stationary magnetic and a strong electromagnetic field is presented. The new formulation, which is applicable to the two dimentional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity method. We model our system as a two dimentional electron gas (2DEG) which interact with two external fields. To incorporate the strong light coupling with the 2DEG, we utilize the Floquet theory to analyse the effect nonperturbatively. Moreover, the Floquet Fermi "golden rule" is adopted to explore the scattering effects for Floquet states in disordered quantum Hall system. Based on our fully analytical expression and paticular graphical representations, we demostrate
that the characteristics of conductivities in two dimentional quantum Hall systems can be manipulated using a dressed field. The outcomes are well align with theoritical descriptions which are already well-suited with experimental results at the same time our theory provide more generalized analysis on the properties of conductivity in quantum Hall systems. Thus, this model more realistically describes that how to use a external strong radiation  as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-optoelectonic devices.
